\documentclass[margin]{res}
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage[utf8]{inputenc}
\begin{document}

\moveleft\hoffset\vbox{\LARGE\bf Carlos Soriano \large\tt <carlos.soriano89@gmail.com>}

\begin{resume}
 
\section{\small OBJECTIVE}
                Research computer science and contribute to OSS
 

\section{\small COMPUTER \\ SKILLS}
                {\sl Concepts:} Computer graphics, Desktop Environments, Core aplications. \\
                {\sl Languages:} Python, C++, JavaScript, Java, CSS, HTML. \\
                {\sl Operating Systems:} Linux. \\
                {\sl Tools:} Git, Eclipse. \\
                {\sl Platforms:} Gnome. \\
 
\section{\small EXPERIENCE} {\sl Researcher} \hfill 2010 - current \\
                GGG, Universitat de Girona, Girona
                \begin{itemize}  \itemsep -2pt
                \item Researching and developing about procedural buildings.
                \end{itemize}
                
                {\sl Contributor} \hfill 2012 - current \\
                GNOME Desktop Environment - OpenGL based desktop for Linux.
                \begin{itemize} \itemsep -2pt
                \item Contributor to Gnome Shell core.
                \item Developer of some Gnome extensions.
                \item Contributor to Gnome Shell wiki.
                \end{itemize}
                
                {\sl Formal teacher} \hfill 2011 - current \\
                Club Tramuntana, Girona
                \begin{itemize}  \itemsep -2pt
                \item Teaching informatics to 10-15 years old kids. 
                \end{itemize}
                
\section{\small EDUCATION}
                {\sl Universitat de Girona:} Ingenyeria informàtica \hfill 2008 - current \\

\section{\small PERSONAL \\ SKILLS}
                \begin{itemize}  \itemsep -2pt
                \item Working with very large projects.
                \item Working with many people in different projects.
                \item Persistent.
                \item Perfeccionist and strict taking into account time available.
                \end{itemize}
                
\section{\small WEBSITES \\ AND \\ CONTACT}
                {\sl GitHub:} http://github.com/csoriano89 \\
                {\sl GGG email:} \tt <csoriano@ima.udg.edu> \\
                {\sl Gnome email:} \tt <csoriano@src.gnome.org> \\

\end{resume}
\end{document}
